A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-04 latex/main.tex
Update

The second primary contribution of this work is the method used to 
infer the ARG, sc2ts. [WIP]

>>>>

The second primary contribution of this work is the method used to 
infer the ARG, sc2ts. The ability to infer an ARG over millions of whole 
genomes is a step change in scale over existing ARG 
inference methods for pathogen data\cite{Didelot2010inference,%
Vaughan2017inferring,%
Muller2020bayesian,%
Ignatieva2022,%
Muller2022bayesian}.
Similarly, detecting and fully incorporating recombination 
in real-time at pandemic scale extends the 
demonstrated utility of a comprehensive
genealogy~\cite{Hinrichs2024,McBroome2024}, clarifying the 
role of recombination and enabling timely analysis.
Given the novelty of sc2ts and the inferred ARG, we have focused 
significant attention here on methodological issues. 
Through these detailed analyses we validate the ARG itself,
ensuring that it is a trustworthy basis for future research,
and deepen our understanding of the inference method, and 
how it may be adapted and improved (see Limitations of Study).

The secondary contributions of this work are the initial 
insights into the evolution of SARS-CoV-2 obtained by studying
the sc2ts ARG. Firstly, we have clarified the relationships among
the recombinant Pango X-lineages, suggesting significant 
clustering of named lineages under shared recombination events.
Secondly, we have used the ARG to study breakpoint intervals 
for recombination events, adding a novel temporal dimension
and demonstrating its theoretical relationship with the 
size of the interval in base pairs. Thirdly,

These underscore the utility of the ARG itself, and suggest
several important directions for future research.
